---
title: "p8105_hw3_bg2604"
author: "Boya Guo"
date: "10/15/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(ggridges)
library(hexbin)
devtools::install_github("thomasp85/patchwork")
theme_set(theme_bw())
```

### Problem 1

```{r p1 Import and clean dataset}
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
p1_brfss=brfss_smart2010 %>%
  janitor::clean_names() %>%
  separate(locationdesc, into = c("state", "county"), sep = " - ") %>%
  filter(topic == 'Overall Health') %>%
  mutate(response = as.factor(response),
         response = factor(response, levels = c("Excellent", "Very good", "Good", "Fair", "Poor"))) %>%
  select(-locationabbr, year, state, county, response, everything())
```

#### Problem 1.1 In 2002, which states were observed at 7 locations?

```{r p1.1}
p1_brfss %>%
  filter(year == 2002) %>% 
  group_by(year, state) %>% 
  summarize(count = n_distinct(county)) %>% 
  filter(count == 7)
```
Answer: According to the R output, CT, FL and NC states were observed at 7 locations.

#### Problem 1.2 Make a “spaghetti plot” that shows the number of locations in each state from 2002 to 2010.

```{r p1.2}
p1_brfss %>% 
  group_by(year, state) %>% 
  summarize(count = n_distinct(county)) %>% 
  ggplot(aes(x = year, y = count, color = state)) + 
  geom_point() + 
  geom_line(alpha = .5) + 
  labs( title = "Locations in each state, 2002-2010",
    x = "Year",
    y = "Number of locations"
    ) + 
  theme(legend.position = "left")
```

#### Problem 1.3 Make a table showing, for the years 2002, 2006, and 2010, the mean and standard deviation of the proportion of “Excellent” responses across locations in NY State.

```{r p1.3}
brfss_p1.3 <- p1_brfss %>%
  spread(key = "response", value = "data_value") %>% 
  janitor::clean_names() %>%
  filter( year == 2002 | year == 2006 | year == 2010) %>%   
  filter(state == "NY") %>% 
  group_by(state, county) %>% 
  summarize(avg_excellent = mean(excellent, na.rm = TRUE),sd_excellent = sd(excellent, na.rm = TRUE)) %>% 
  knitr::kable(digits = 1)

brfss_p1.3
```

#### Problem 1.4 For each year and state, compute the average proportion in each response category (taking the average across locations in a state). Make a five-panel plot that shows, for each response category separately, the distribution of these state-level averages over time.

```{r p1.4}
p1_brfss %>% 
  spread(key = "response", value = "data_value") %>% 
  janitor::clean_names() %>% 
  select(year, state, county, excellent:poor) %>% 
  group_by(year, state) %>% 
  summarize(mean_excellent = mean(excellent, na.rm = TRUE),
            mean_very_good = mean(very_good, na.rm = TRUE),
            mean_good = mean(good, na.rm = TRUE),
            mean_fair = mean(fair, na.rm = TRUE),
            mean_poor = mean(poor, na.rm = TRUE)
            ) %>% 
  gather(key = "mean_response", value = "average_proportion",    
  mean_excellent:mean_poor) %>%
  mutate(mean_response = as.factor(mean_response),
  mean_response = factor(mean_response, levels = c("mean_excellent", "mean_very_good", "mean_good", "mean_fair", "mean_poor"))) %>% 
  ggplot(aes(x = year, y = average_proportion, color = state)) + 
  geom_point() + geom_line() +
  facet_grid(~mean_response) +
  labs(
    title = "Average proportion in each overall health response for years and states",
    x = "Year",
    y = "Average proportion"
  ) + theme(legend.position = "none",axis.text.x = element_text(angle = 45))
```

### Problem 2

Write a short description of the dataset, noting the size and structure of the data, describing some key variables, and giving illstrative examples of observations. 

#### Problem 2.1 How many aisles are there, and which aisles are the most items ordered from?

```{r p2.1}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_item = n()) %>% 
  arrange(desc(n_item))
```

Answer: There are 134 aisles in the dataset. The fresh vegtables, frresh fruits, packaged vegetables fruits are the top three aisles with the most items ordered. 

#### Problem 2.2 Make a plot that shows the number of items ordered in each aisle. Order aisles sensibly, and organize your plot so others can read it.

```{r p2.2}
instacart_p2.2 <- instacart %>% 
  group_by(aisle) %>% 
  summarize(item_count = n()) %>% 
  mutate(group = as.numeric(cut_number(item_count, 3))) %>% 
  ggplot(aes(x = aisle, y = item_count)) +
    geom_point() +
    facet_wrap(group ~ ., nrow = 3, scales = "free") +
    theme(axis.text.x = element_text(size = 6, hjust = 1, angle = 50)) +
    labs(
      title = "Number of items ordered in aisles",
      x = "Aisle Name",
      y = "Number of Items Ordered"
      )
instacart_p2.2
```

#### Problem 2.3 Make a table showing the most popular item in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”.

```{r p2.3}

```


